Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-02-27 sections/introduction.tex
I changed some wording in the Introduction

Our goal with this project is to determine the size of the radio solar disc by using observations during the April 8th, 2024 Total Solar Eclipse.
This eclipse gave us a unique opportunity to observe the outer atmosphere of the sun without the solar disc overwhelming our ground-based radio telescope. % Check spelling of disc
To accomplish this, we need to determine how much of the solar disc is obscured by the moon during totality in both the optical and radio wavelengths.
We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
To verify these results, we have multiple sources of optical lightcurve data:
\begin{itemize}
    \item Livestream from the UCA Observatory
    \item Broad-spectrum light sensor pointed at the sky, also at UCA
    \item Theoretical lightcurve generated by Stellarium
\end{itemize}% I don't like how much space there is between bullets

>>>>

Our goal with this project is to determine the size of the radio solar disk by using observations during the April 8th, 2024 Total Solar Eclipse.
This eclipse gave us a unique opportunity to observe the outer atmosphere of the sun without overwhelming our ground-based radio telescope.
To accomplish this, we need to determine how much of the solar disk is obscured by the moon during totality in both the optical and radio wavelengths.
We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
To verify these results, we have multiple sources of optical lightcurve data:
\begin{itemize}
    \item Livestream from the UCA Observatory
    \item Broad-spectrum light sensor pointed at the sky, also at UCA
    \item Theoretical lightcurve generated by Stellarium
\end{itemize}% I don't like how much space there is between bullets
